The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-06 analysis/paper/paper.qmd
Format code
Remove lemmatization attempts from bigrams code chunk

## Read metadata for all theses
all_theses <-
  readxl::read_xlsx(path = here(data_path, "theses-all.xlsx"))

@@

spacyr::spacy_parse(emu_bigrams$w_1)
data.frame(emu_bigrams$w_1, textstem::lemmatize_words(emu_bigrams$w_1))

set.seed(12345)

# with spacy
extract_rand_window <- function(x, p){
    first_index = sample(seq(length(x) - p + 1), 1)
    x[first_index:(first_index + p -1)]
    }

example_lemma <-list()
for (i in 1:10) {
  example_lemma[[i]] <- extract_rand_window(emu_bigrams$w_1,10)
}

Original <- unlist(example_lemma)
Lemmatized <- spacyr::spacy_parse(Original)

# with textstem
Lemmatized2 <- textstem::lemmatize_words(Original)

lemma_example <- data.frame(Original, Lemmatized2)

lemma_example

data.frame(Lemmatized$token, Lemmatized$lemma, Lemmatized2)

>>>>

## Read metadata for all theses
all_theses <- read_xlsx(path = here(data_path, "theses-all.xlsx"))

@@
